Hierarchically Supervised Latent Dirichlet Allocation

### 2011-06-02 paper/experiments.tex
Added to experiments section

>>>>

The following are the predictive performance results for the clinical
data given a prior mean for the regression parameters of -1.6. 
The full HSLDA model had a true positive rate of 0.57 
and a false positive rate of 0.13, the sLDA model had a true positive
rate of 0.42 and a false positive rate of 0.07, and the HSLDA model where
LDA and the regressions were fit separately had a true positive rate of 0.39
and a false positive rate of 0.08.

These results indicate that the full HSLDA model predicts more of the the
correct labels at a cost of an increase in the number of false positives
relative to the comparison models.

The following are the predictive performance results for the retail product
data given a prior mean for the regression parameters of -2.2. 
The full HSLDA model had a true positive rate of 0.85 
and a false positive rate of 0.30, the sLDA model had a true positive
rate of 0.78 and a false positive rate of 0.14, and the HSLDA model where
LDA and the regressions were fit separately had a true positive rate of 0.77
and a false positive rate of 0.16. These results follow a similar pattern to the clinical data.

To further explore this tradeoff between the true positive rate and the
false positive rate we evaluated predictive performance for a range of values
for two different parameters - the prior mean for the regression coefficients
and the threshold for the auxiliary variables.  The goal in this analysis
was to evaluate the performance of these models subject to more or less
stringent requirements for predicting positive labels. These two parameters 
have important related functions in the model. The prior mean in combination 
with the auxiliary variable threshold together encode the strength of the prior
belief that unobserved labels are likely to be negative. Effectively, the
prior mean applies negative pressure to the predictions and the auxiliary
variable threshold determines the cutoff.

For each model type, separate models were fit for each value of the 
prior mean of the regression coefficients.  In contrast, to evaluate
predictive performance as a function of the auxiliary variable threshold,
a single model was fit for each model type and prediction was evaluated
based on predictive samples drawn subject to different auxiliary variable
thresholds. These methods are significantly different since the prior mean
is varied prior to inference and the auxiliary variable threshold is varied
after inference.  However, as intended, they both highlight model performance
under more or less stringent requirements for predicting positive labels.

Figures \ref{fig:main_clinical_results} and \ref{fig:main_amazon_results} show the predictive performance
of HSLDA relative to the three comparison models.
